---
title: ""
---

## Aims & scope


The R Journal is a peer-reviewed, open-access scientific journal, published by The R Foundation. It features short- to medium-length articles (up to 20 pages) covering topics of interest to users and developers of R. For example, description and implementation details of R packages, surveys or reviews of R software related to a particular area, applications of R software or descriptions of teaching resources related to R.

All submissions must primarily be about R packages and R programming. Submissions that involve R calling other software will be considered provided: (a) the other software is open source and free to use; (b) is widely used; and (c) there is a clear justification for using it rather than a native R implementation. Occasional exceptions may be made if (a) is not satisfied, provided there is no viable open source alternative.

The R Journal reaches a wide audience and has a thorough review process. It has a generally increasing [SJR impact factor](https://www.scimagojr.com/journalsearch.php?q=21100255423&amp;tip=sid&amp;exact=no). For article types, R package paper guidelines, and submission instructions, see [For authors](contribute_authors.html).

## History

The R Journal was established in 2009, superseding the [R News](http://www.r-project.org/doc/Rnews/index.html).  For historical purposes it also includes a news section, that includes items from R Core, updates from CRAN and Bioconductor, foRwards activities and conference reports.

## Submission statistics

The R Journal receives around 150 a year, and processing times and especially review times are highly variable. The summaries below shows that for published articles, the time from first submission to accept averages at under a year.

```{r, echo=FALSE, eval=FALSE}
# To update plots below, run from the articles project. The code uses tabulate_articles, which runs only from articles.

article_status_plot()
time_to_accept_plot()
```

```{r, echo=FALSE}
years <- rev(as.numeric(format(Sys.Date(), "%Y")) - (1:4))

```

```{r, echo=FALSE, fig.height=3, out.width=c("44%", "56%"), fig.show="hold"}
plots <- c(
  "../assets/time_to_accept_plot.png",
  "../assets/article_status_plot.png"
)
if (all(file.exists(plots))) {
  knitr::include_graphics(plots)
}
# published articles here refers to all in the Proofs folder. Which will coincide with website when published.
```

For published articles in the years `r years`, the boxplots show time from submission to accept by year of publication. Median number of days to accept is under a year. The barchart on the right refers to articles submitted in the years `r years`, and reports the status as rejected, in progress or accepted/published. Papers labelled 'in progress' are under review or awaiting revisions.
